\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\signature{Saul Burgess}

\begin{document}

\begin{letter}{}


\noindent\begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}} \textbf{Sender's
    Address:} & \textbf{Receiver's Address:} \\
    49 Sefton Green, & BearingPoint Ireland, \\
    Rochestown Avenue, & Montague House, \\
    Dun Laoghaire, & Adelaide Road, \\
    A96 NV96 & Saint Kevin's, \\
    & Dublin 2 \\
    \end{tabular}


\opening{To whom it may concern,}

I am excited to apply for the 2025 Graduate Opportunities-Software Development
Position at BearingPoint Ireland. As a recent graduate with a Masters Degree in
Computer Science from Technological University Dublin, I am eager to bring my
passion for coding, problem-solving, and innovation to your team.

During my University experience, I developed strong foundations in programming
languages such as Typescript, Java and Go and honed my skills in software
development, algorithms, and database management. A key highlight of my studies
was my Master's Thesis, where I developed a web application called Magpie, which
served as a Geographical Information System for Local Authorities to assist them
in planning developments. Magpie was developed as a Microservice-First
application, with database and backend services. This experience taught me the
importance of writing clean, efficient code and as Team lead, collaborating
effectively to meet deadlines.

Beyond academics, I actively pursue personal projects to expand my skills. For
example, I run an extensive Kubernetes based home lab, I use this primarily to
host local services, such as media archiving and single-sign-on, demonstrating
my initiative and commitment to continuous learning.

I am particularly inspired by BearingPoint’s dedication to collaboration and
sustainability and your belief that ``together we are more then business'', and I
am eager to apply my technical expertise to contribute to your projects.

Although I am at the beginning of my professional career, my enthusiasm for
software development, combined with a strong work ethic and ability to adapt
quickly, positions me to grow and thrive as a part of your team. I am very eager
to learn from experienced colleagues, whether on-site or remotely, while
contributing fresh perspectives and creative solutions.

Thank you for considering my application. I would welcome the opportunity to
discuss how my skills and passion align with BearingPoint’s values. I have
attached my CV and look forward to the possibility of contributing to your team.

\closing{Yours sincerely,}

\end{letter}

\end{document}
