%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV XeLaTeX Template Version 1.0 (22/1/2015)
%
% This template has been downloaded from: http://www.LaTeXTemplates.com
%
% Original author: Howard Wilson (https://github.com/watsonbox/cv_template_2004)
% with extensive modifications by Vel (vel@latextemplates.com)
%
% License: CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Saul Burgess -- Curriculum Vitae} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
    \begin{tabbing} % Enables tabbing
        \hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
        {\bf Address} \> 49 Sefton Green,\\ % Address line 1
        \> Rochestown Avenue, \\
        \> Dun Laoghaire, Co. Dublin \\ % Address line 2
        \> A96 NV96 \\
    \end{tabbing}} \hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
    \begin{tabbing} % Enables tabbing
        \hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
        {\bf Date of Birth} \> 27$^{th}$ September 2000 \\ % Date of birth 
        {\bf Mobile Phone} \> +353 86 189 4828 \\ % Mobile phone
        {\bf Email Address} \>
        \href{mailto:burgesssaul@gmail.com}{burgesssaul@gmail.com} \\ % Email
        \end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

I am a Software Developer with 1 formal years of experience implementing front
\& backend services. I have a strong understanding of the full software
development lifecycle, including Agile, Test-Driven-Development, and DevOps. I
am experienced in developing and implementing web applications using modern
technologies such as Java, Node and React. I am also experienced in developing
and maintaining databases, and have a strong understanding of the principles of
software design and architecture.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{ \bf{2023--2024} \> MSc (Hons) Computer Science - Advanced Software
Development\\[5pt]
\>\+ Technological University Dublin }

%------------------------------------------------

\tabbedblock{ \bf{2019--2023} \> BSc (Hons) Computer Science \\[5pt]
% \bf{Modules Completed:} \\
% \textbullet Software Development, \textbullet Databases, \textbullet Human
% Computer Interaction, \textbullet Microprocessors, \\
% \textbullet Embedded Systems, \textbullet Internet Applications and Web
% Development, \textbullet Networking Systems Administration, \\
% Mobile Software Development, Web Development 2, Cloud Computing, Databases 2,
% DevOps, SysInfra \\
% Advanced Security, Machinen Learning, Distributed Systems, Systems Integration
% \\
\>\+ Technological University Dublin }

%------------------------------------------------

\tabbedblock{ \bf{2013--2019} \> Honours Leaving Certificate - St. Conleth's
    College\\[5pt]
    \>\+ Ballsbridge, Dublin 4 }

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

%------------------------------------------------

\job
{May 2023}{- Sep 2023} {Accenture, Grand Canal Quay} {http://www.accenture.com}
{Summer Internship - Technical Analyst} {Focused on Software Development and
Application Development.}

%------------------------------------------------

\job
{Jan 2022}{- Sep 2022} {Department of Agriculture, Food, and the Marine}
{http://www.agriculture.gov.ie} {Junior Software Developer} {Third-year
placement for 20 weeks, extended by the Dept. until TUD 4th Year term commenced
Computer Science undergraduate degree program. Retained until University 2022
Autumn term. Worked with Typescript, Java Spring and Continuous Integration
(Development) platforms to develop a disease management application for the
department.}

%------------------------------------------------

\job
{Jul 2019}{- Aug 2019} {Rockall Technologies, Dun Laoghaire (part of Broadridge
Financial Solutions)} {http://www.rockalltech.com} {Development \& Test Intern}
{}

%------------------------------------------------

% \job {May 2017 -}{May 2017} {Department of Higher Education}
% {http://www.education.ie} {Intern} {Worked with then Minister Mary Mitchell
% O’Connor. Assisted in clerical duties, writing briefs on county
% representatives.}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------
\newpage
\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
    \begin{tabular}{l l}
        \textbf{Language} & \textbf{Versions/Technologies} \\
        JavaScript & ES6 \\
        TypeScript & 5.x \\
        Java & jdk 21, jdk 20, jdk 17 \\
        Python & 3.12, 2.7 \\
        C++ & 17 \\
        Go & 1.23 \\
    \end{tabular}
}

\skillgroup{Projects}{
    \begin{itemize}
        \item \textbf{Magpie - GIS} \\
        As part of my Masters Thesis, I developed a single-page application with
        Go, Python and Next.js. Implementing a Geographical Information System.

        Magpie utilises Machine Learning to detect parking spaces from satellite
        imagery, this coupled with other public data sources allows Civil
        Planners to view GIS data and make informed decisions based on the data.

        \href{https://github.com/2024-CMPU9010-GROUP-3/magpie}{GitHub Repository
        (link)},
        \href{https://www.linkedin.com/in/saulburgess/details/featured/}{Thesis (link)}

        \vspace{5pt}

        \item \textbf{Kubernetes Home Lab} \\
        Run using Kubernetes, Flux and GitOps. This project supports my other
        projects. While the manifests are publicly hosted, I make use of various
        GitOps strategies to ensure that secrets remain secret.

        \href{https://github.com/1Solon/Home-Server-Configuration}{GitHub
        Repository (link)}

        \vspace{5pt}

        \item \textbf{TreeMD} \\
        A Go-based utility that prints a visual representation of a directory
        tree. It supports excluding specified directories and displaying the
        tree up to a certain depth. It includes support for GitHub actions,
        allowing a Markdown file to be updated with new file structure changes.

        \href{https://github.com/1Solon/treemd}{GitHub Repository (link)}
    \end{itemize}
}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests \& Acomplishments}

\interestsgroup{
    \interest{Represented TUD in Games Fleadh 2020, a java based
    Artificial Intelligence challenge ‘Robocode’ having designed and written
    ‘Oberon’, a decision tree based, linear targeting virtual tank.} \\

    \interest{CoderDojo Mentor (Dun Laoghaire) – member since 2012. Youngest
        appointed student mentor in 2016 – privileged to have the opportunity to
        guide the next generation of young coders and developers.} \\

    \interest{Skilled Public Speaker – second place in the Trinity Classics
        Oratory competition for three consecutive years.} \\

    \interest{Accomplished Sailor, achieved my Royal Yachting Association Level
        Three Grade during my fourth year of secondary school.}

}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

% \section{Referees}

% \parbox{0.5\textwidth}{ % First block \begin{tabbing} \hspace{2.75cm} \=
%     \hspace{4cm} \= \kill % Spacing within the block {\bf Name} \> Bill
%     Lumbergh \\ % Referee name {\bf Company} \> Initech Inc. \\ % Referee
%     company {\bf Position} \> Vice President \\ % Referee job title {\bf
%     Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee
%     contact information \end{tabbing}} \hfill % Horizontal space between the
%     two blocks \parbox{0.5\textwidth}{ % Second block \begin{tabbing}
%     \hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block {\bf
%     Name} \> Michael "Big Mike" Tucker\\ % Referee name {\bf Company} \>
%     Burbank Buy More \\ % Referee company {\bf Position} \> Store Manager \\ %
%     Referee job title {\bf Contact} \>
%     \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact
%     information \end{tabbing}}

% %----------------------------------------------------------------------------------------

\end{document}