\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\signature{Saul Burgess}

\begin{document}

\begin{letter}{}

\noindent\begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}} \textbf{Sender's
    Address:} & \textbf{Receiver's Address:} \\
    49 Sefton Green, & Ryanair Ireland, \\
    Rochestown Avenue, & Ryanair Dublin Office, \\
    Dun Laoghaire, & Airside Business Park, Swords, \\
    A96 NV96 & Co. Dublin, Ireland \\
    \end{tabular}

\opening{To whom it may concern,}

I am excited to apply for the Software Engineering Graduate position at Ryanair
Ireland. As a recent graduate with a Master’s Degree in Computer Science from
Technological University Dublin, I am eager to bring my passion for efficient
and scalable software systems and innovative problem-solving to your team.

During my university experience, I developed strong foundations in programming
languages such as TypeScript, Java, and Go, honing my skills in software
development, algorithms, and database management. A key highlight of my studies
was my Master's Thesis, where I developed a web application called Magpie,
serving as a Geographical Information System for Local Authorities to assist in
planning developments. Magpie was developed as a Microservice-First application
with database and backend services. This experience taught me the importance of
writing clean, efficient code and, as Team Lead, collaborating effectively to
meet deadlines.

Beyond academics, I actively pursue personal projects to expand my skills. For
example, I run an extensive Kubernetes-based home lab, hosting local services
such as media archiving and single-sign-on, demonstrating my initiative and
commitment to continuous learning.

I am particularly inspired by Ryanair’s commitment to innovation and operational
excellence in the airline industry. Your focus on leveraging technology to
provide efficient, customer-focused services aligns perfectly with my interest
in building scalable and impactful systems. I am eager to apply my technical
expertise to contribute to Ryanair’s projects and mission.

Although I am at the beginning of my professional career, my enthusiasm for
software development, combined with a strong work ethic and ability to adapt
quickly, positions me to grow and thrive as a part of your team. I am eager to
learn from experienced colleagues, whether on-site or remotely, while
contributing fresh perspectives and creative solutions.

Thank you for considering my application. I have attached my CV and look forward
to the opportunity to discuss how my skills and passion align with Ryanair
Ireland’s values. I would be delighted to contribute to your mission of
providing exceptional value to customers through technology-driven efficiency.

\closing{Yours sincerely,}

\end{letter}

\end{document}
